---
title: "Recommender Systems Study Design"
author: "Yaqi Zhou; Yanan Huo; Li Luo; Kejia Shi"
date: "March 2, 2016"
output: beamer_presentation
---

##Introduction & Key Questions

1. Predicting ratings using algorithms in the `recommenerlab` package and other machine learning approaches;

2. Comparing these methods.



## Plan of Approach

1) Data visualization and relationship exploration

• Is there any relationship between rating and information about films, e.g. genre, as well as demographic variables, e.g. age, occupation, gender and zip_code?

2) Approach 1: Rating prediction using R/recommenderlab package

3) Approach 2: Rating prediction using other machine learning approaches

4) Evaluation of rating predictions and method comparison




## rating vs. age vs. occupation

```{r,echo=FALSE,warning=FALSE,message=FALSE}
library(recommenderlab)
library(ggplot2)
data<-read.csv("unifiedMLDataMulti.csv",head=T)
ggplot(data, aes(x=as.factor(rating),y=age)) +
    geom_boxplot(aes(fill=as.factor(rating))) +
    scale_fill_discrete(name="rating") +
    facet_wrap(~occupation)+xlab("rating")
```


## genre vs.occupation vs. rating

```{r, echo=FALSE,message=FALSE,warning=FALSE}
library(RColorBrewer)
library(grid)
library(plyr)
library(dplyr)
mlDat_genre_occup <- ddply(data, ~genre + occupation, summarize, mean_rating = mean(rating))
heatMapPalette <- colorRampPalette(rev(brewer.pal(11, "RdBu")))
goHeat2 <- ggplot(mlDat_genre_occup, aes(x = genre, y = occupation, fill = mean_rating))
goHeat2 <- goHeat2 + geom_tile() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
goHeat2 <- goHeat2 +  scale_fill_gradientn(limits = c(2.5,4.6), colours = heatMapPalette(100))
goHeat2 <- goHeat2 + theme(panel.background = element_rect(fill='darkgreen'), 
                           panel.grid.major = element_blank(), 
                           panel.grid.minor = element_blank())
print(goHeat2)
```

## Normalization

```{r,echo=FALSE,fig.align='center'}
data(MovieLense)
m<-normalize(MovieLense,method="Z-score")
image(MovieLense,xlim=c(0,10),ylim=c(0,10),main="Image plot of unnormalized rating")
```

## Normalization

```{r,echo=FALSE,fig.align='center'}
image(m,xlim=c(0,10),ylim=c(0,10),main="Image plot of normalized rating")
```
